What's hot and what's not:\\Windowed developer topic analysis

### 2009-04-11 lda-paper.tex
lame

Once we have our topics extracted for each window, we analyze them and
look for topics that recur across windows. Our input for topic
similarity is the top 10 most common words of each topic.

We then cluster these topics into trends by comparing them to each
other.  Each topic is compared to each other topic in the system,
given a certain threshold of top 10 similarity, such as 8 out of 10
words. Then given this topic similarity matrix, we find the transitive
closure of similar topics; that is, if we model topics are nodes and
arcs as similarity, we fill flood along the similarity arcs until we
have partitioned the topics into clusters of similar topics. Figure
\ref{fig:closure} illustrates clustering of topics by 
topic similarity. These clusters of topics are called trends. A trend
is probably interesting if it contains more than one topic.

>>>>

Once we have our topics extracted for each window, we analyze them and
look for topics that recur across windows.  We then cluster these
topics into trends by comparing them to each other using topic similarity.

Our input for topic similarity is the top 10 most common words of each
topic.  Each topic is compared to each other topic in the system,
given a certain threshold of top 10 word similarity, such as 8 out of
top 10 matching words. Then given this topic similarity matrix, we
find the transitive closure of similar topics; that is, if we model
topics are nodes and arcs as similarity, we fill flood along the
similarity arcs until we have partitioned the topics into clusters of
similar topics. Figure \ref{fig:closure} illustrates clustering of
topics by topic similarity. These clusters of topics are called
trends. A trend is probably interesting if it contains more than one
topic.
